---
title: 'Research synthesis: Use of computer simulations for environmental education'
author: "Peter Reimann & Peter Freebody"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
always_allow_html: true
---

```{r include=FALSE}
# devtools::install_github("baasman/allegRo") # only on first install
library(kableExtra)
library(allegRo)
library(tidyverse)
# library(knitr)
library(urltools)
```

```{r include=FALSE}
stripOffNS <- function(df) {
  df <- lapply(df, function(x) {gsub(">", "", x)})
  df <- lapply(df, function(x) {gsub("<", "", x)})
  df
}
```

```{r global_options, include=FALSE}
# This is a way to set options for all code chunks at once
# Note that you can also dynamically control options by setting them to a value

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE,
                      dev="png", fig.width = 10, fig.height = 7)
```

```{r include=FALSE}
url = "http://learn-web.com"
user = "anonymous"
password = ""
service = service(url, user, password, testConnection = TRUE)
```

```{r include=FALSE}
cat = catalog(service, "coolfutures")
rep = repository(cat, "compumod")
addNameSpace(repo = rep, prefix= "lrmi", nsURI = "http://purl.org/dcx/lrmi-terms/")
addNameSpace(repo = rep, prefix= "arg", nsURI = "http://www.coolfutures.net/rdf/Design_Conjectures/toulminarg#>")
```


## Method

## Literature search process

The main source is [ERIC](http://eric.ed.gov) because of its focus on
educational research and because it uses a controlled vocabulary
(descriptors). The two constraints on ERIC searches were (a) peer
reviewed journal publications that are (b) published in the English
language.

ERIC search tearms and results

+-------------------------------+--------------------------------------+
| Query                         | Results                              |
+===============================+======================================+
| (1)                           | 79                                   |
| descriptor:"environmental     |                                      |
| education" AND                |                                      |
| descriptor:"computer          |                                      |
| simulation"                   |                                      |
+-------------------------------+--------------------------------------+
| (2)                           | 11 results, seven of which           |
| descriptor:"environmental     | overlapping with (1).                |
| education" AND                |                                      |
| descriptor:"computer model"   |                                      |
+-------------------------------+--------------------------------------+
| (3)                           | 54 results largely not overlapping   |
| descriptor:"environmental     | with (1) and (2), and indeed more    |
| education" AND                | general in technology formats.       |
| descriptor:"Technology        |                                      |
| integration"                  |                                      |
+-------------------------------+--------------------------------------+
| (4)                           | Does not yield additional studies    |
| Replacing “environmental      | that include computer simulations.    | 
| education” with “climate      |                                       |
| change education” in (1)-(3)  |                                     |
| education"                    |                                      |
+-------------------------------+--------------------------------------+



### Coding

Coding category frequencies:

```
SELECT  ?scheme (COUNT(?concept) as ?theCount)
    WHERE { ?scheme a skos:ConceptScheme. 
      ?concept skos:inScheme ?scheme}
   GROUP BY ?scheme
```


The result of the coding in one table:

```{r include=FALSE}
query = 'SELECT ?work ?p ?o
 
WHERE {
  ?work a dc:BibliographicResource.
  ?o a skos:Concept . 
  ?work ?p ?o . 
 }
ORDER BY ?work'

workTable <- evalQuery(rep,
query = query, returnType = "dataframe",
cleanUp = TRUE, convert = TRUE) 
```

```{r include=FALSE}
wTab <- as.data.frame(workTable[1])
# Rename the columns 
colnames(wTab) <- c("work", "category", "code")
```

```{r include=FALSE}
# Stripp of URIs
#wTab <- data.frame(lapply(wTab, function(x) {gsub(">", "", x)}))
# wTab <- data.frame(lapply(wTab, function(x) {gsub("<", "", x)}))
wTab <- stripOffNS(wTab)
wTab$work <- fragment(wTab$work)
wTab$category <- fragment(wTab$category)
wTab$code <- fragment(wTab$code)
```


```{r warning=FALSE, include=FALSE}
wTab <- as_tibble(wTab)
wTabWide <- wTab %>%
  pivot_wider(names_from = category, values_from = code)
```


```{r}
# Drop the column modelDesign and display table
wTabWide$modelDesign <- NULL
# kable(wTabWide, caption = "Table: Categories by Studies.")
wTabWide %>%
  kbl(caption = "Categories by works") %>%
  kable_paper(bootstrap_options = c("striped", "condensed"), full_width = T)
```

## Descriptive quantitative findings

### Publications by year

The distribution of publications over the years is as follows. 


```{r}
query = 'SELECT ?year (COUNT(?year) AS ?yearTotal)
        WHERE
	{ 
    ?work dc:date ?year .
    }
GROUP BY ?year 
ORDER BY DESC(?year) '

yearTable <- evalQuery(rep, query = query, returnType = "dataframe", cleanUp = TRUE, convert = TRUE)

prtTable <- as.data.frame(yearTable[1])
colnames(prtTable) <- c("year", "count")
# create a percentage column
prtTable$count <- as.numeric(as.character(prtTable$count))
prtTable <- mutate(prtTable, percentage = round((count / sum(count))*100, 1))
# Render the table. 
prtTable %>%
  kbl(caption = "Publications by year") %>%
  kable_paper(full_width = F)
```

In graphical form:


```{r, fig.cap = "Publications by year"}
df <- as.data.frame(yearTable[1])
ggplot(df,aes(return.year, return.yearTotal) ) +
  geom_col() + 
  xlab("Year") +
  ylab ("Count") +
 ggtitle ("Number of publications by year.")
```


### Student age groups

```
SELECT  ?concept (COUNT(?work) AS ?workCount) 
WHERE 
{
    :MiddleSchools skos:narrower* ?concept.
    ?work ?p ?concept; a dc:BibliographicResource
}
GROUP BY ?concept
```

```{r countEducationLevels}
# count Primary
query = 'SELECT  (COUNT(?work) AS ?workCount) 
WHERE 
{
    {:PrimaryEducation skos:narrower* ?concept.
    ?work :educationalLevel ?concept.}

}'
qReturn <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE, convert = TRUE) 
schoolPrimary <- qReturn[["return"]][["workCount"]]

#Count Middle
query = 'SELECT  (COUNT(?work) AS ?workCount) 
WHERE 
{
    {:MiddleSchools skos:narrower* ?concept.
    ?work :educationalLevel ?concept.}

}'
qReturn <- evalQuery(rep,
query = query, returnType = "dataframe",
cleanUp = TRUE, convert = TRUE) 
schoolMiddle <- qReturn[["return"]][["workCount"]]

#Count Highschool
query = 'SELECT  (COUNT(?work) AS ?workCount) 
WHERE 
{
    {:HighSchools skos:narrower* ?concept.
    ?work :educationalLevel ?concept.}

}'
qReturn <- evalQuery(rep,
query = query, returnType = "dataframe",
cleanUp = TRUE, convert = TRUE) 
schoolHigh <- qReturn[["return"]][["workCount"]]

#Count Higher Ed
query = 'SELECT  (COUNT(?work) AS ?workCount) 
WHERE 
{
    {:HigherEducation skos:narrower* ?concept.
    ?work :educationalLevel ?concept.}

}'
qReturn <- evalQuery(rep,
query = query, returnType = "dataframe",
cleanUp = TRUE, convert = TRUE) 
schoolTertiary <- qReturn[["return"]][["workCount"]]

#Count Adult ed
query = 'SELECT  (COUNT(?work) AS ?workCount) 
WHERE 
{
    {:Adults skos:narrower* ?concept.
    ?work :educationalLevel ?concept.}

}'
qReturn <- evalQuery(rep,
query = query, returnType = "dataframe",
cleanUp = TRUE, convert = TRUE) 
schoolAdult <- qReturn[["return"]][["workCount"]]

# Finally gather in a df 
levelsDF <- data.frame(EduLevel = c("Primary", "MiddleSchool", "HighSchool", "HigherEducation", "Adult"), freq = c(schoolPrimary, schoolMiddle, schoolHigh, schoolTertiary, schoolAdult))
```

```{r include=FALSE}
# create a percentage column
levelsDF <- mutate(levelsDF, percentage = round((freq / sum(freq))*100, 1))
```


```{r}
levelsDF %>%
  kbl(caption = "Educational levels") %>%
  kable_paper(full_width = F)
```



### Science areas


```{r include=FALSE}
query = 'SELECT ?science (COUNT(?science) AS ?scienceTotal)
        WHERE
	{ 
    ?work :science ?science .
    }
GROUP BY ?science  
ORDER BY ?science '
scienceTable <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE)
prtTable <- as.data.frame(scienceTable[1])
colnames(prtTable) <- c("science", "count")
```

```{r include=FALSE}
# Stripp of URIs
prtTable <- as.data.frame(stripOffNS(prtTable))
prtTable$science <- fragment(prtTable$science)
```


```{r include=FALSE}
# create a percentage column
prtTable$count <- as.numeric(as.character(prtTable$count))
prtTable <- mutate(prtTable, percentage = round((count/sum(count))*100, 1))
```

```{r}
prtTable %>%
  kbl(caption = "Science areas addressed") %>%
  kable_paper(full_width = F)
```



### Learning outcomes targeted

```{r}
query = 'SELECT ?outcome (COUNT(?outcome) AS ?outcomeTotal)
        WHERE
	{ 
    ?work :outcome ?outcome .
    }
GROUP BY ?outcome  
ORDER BY ?outcome '
outcomeTable <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE)
prtTable <- as.data.frame(outcomeTable[1])
colnames(prtTable) <- c("outcome", "count")
```

```{r include=FALSE}
# Stripp of URIs
prtTable <- data.frame(stripOffNS(prtTable))
prtTable$outcome <- fragment(prtTable$outcome)
```


```{r include=FALSE}
# create a percentage column
prtTable$count <- as.numeric(as.character(prtTable$count))
prtTable <- mutate(prtTable, percentage = round((count/sum(count))*100, 1))
```

```{r}
prtTable %>%
  kbl(caption = "Learning outcomes") %>%
  kable_paper(full_width = F)
```





### Types of simulations and pedagogical strategies

#### Types of simulations and other technologies 

##### Overview

```{r}
# All tech

query = 'SELECT  (COUNT(?work) AS ?workCount) 
WHERE 
{
    ?concept a skos:Concept.
    ?work :technology ?concept.
} '
qReturn <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE, convert = TRUE) 
techAll <- qReturn[["return"]][["workCount"]]

# All types of computer models
query = 'SELECT  (COUNT(?work) AS ?workCount) 
WHERE 
{
  :ComputerModel skos:narrower* ?concept.
  ?work :technology ?concept . 

}' 
qReturn <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE, convert = TRUE) 
techCompModels <- qReturn[["return"]][["workCount"]]

# All immersive tech 
query = 'SELECT  (COUNT(?work) AS ?workCount) 
WHERE 
{
  :ImmersiveTech skos:narrower* ?concept.
  ?work :technology ?concept . 

}' 
qReturn <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE, convert = TRUE) 
techImmersive <- qReturn[["return"]][["workCount"]]

# All multimedia tech 
query = 'SELECT  (COUNT(?work) AS ?workCount) 
WHERE 
{
  :MultiMedia skos:narrower* ?concept.
  ?work :technology ?concept . 

}' 
qReturn <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE, convert = TRUE) 
techMultimmedia <- qReturn[["return"]][["workCount"]]

# All eResearch tech 
query = 'SELECT  (COUNT(?work) AS ?workCount) 
WHERE 
{
  :eResearch skos:narrower* ?concept.
  ?work :technology ?concept . 

}' 
qReturn <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE, convert = TRUE) 
techEResearch <- qReturn[["return"]][["workCount"]]

# Finally gather in a df 
techDF <- data.frame(tech = c("Any technology", "ComputerModels", "ImmersiveTech", "Multimedia", "eResearch"), freq = c(techAll, techCompModels, techImmersive, techMultimmedia, techEResearch))
```



```{r}
techDF %>%
  kbl(caption = "Learning technologies overview") %>%
  kable_paper(full_width = F)
```


##### Studies with 3 or more technologies

```
query = 'SELECT  ?work (COUNT(?tech) as ?techCount)
WHERE 
{
    ?work a dc:BibliographicResource . 
    ?work :technology ?tech .
}

GROUP BY ?work
ORDER BY DESC(?techCount)'
```


##### Types of simulations 


```{r}
query = 'SELECT ?concept (COUNT(?work) AS ?techTotal)
        WHERE
	{ 
    :ComputerModel skos:narrower+ ?concept.
    ?work :technology ?concept .
    }
GROUP BY ?concept  
ORDER BY ?concept '
modelTable <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE)
prtTable <- as.data.frame(modelTable[1])
colnames(prtTable) <- c("modelType", "count")
```

```{r include=FALSE}
# Stripp off URIs
prtTable <- data.frame(stripOffNS(prtTable))
prtTable$modelType <- fragment(prtTable$modelType)
```


```{r include=FALSE}
# create a percentage column
prtTable$count <- as.numeric(as.character(prtTable$count))
prtTable <- mutate(prtTable, percentage = round((count/sum(count))*100, 1))
```

```{r}
prtTable %>%
  kbl(caption = "Simulation and modelling subtypes") %>%
  kable_paper(full_width = F)
```


 
```{r}
# demonstration models 
query = 'SELECT (COUNT(?work) AS ?workCount)
        WHERE {?work :technology :DemonstrationModel } ' 
qReturn <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE, convert = TRUE) 
d1 <- qReturn[["return"]][["workCount"]]

# science models 
query = 'SELECT (COUNT(?work) AS ?workCount)
        WHERE {?work :technology  :DataBasedModel} ' 
qReturn <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE, convert = TRUE) 
d2 <- qReturn[["return"]][["workCount"]]

# datea models 
query = 'SELECT (COUNT(?work) AS ?workCount)
        WHERE {?work :technology  :ScienceBasedModel} ' 
qReturn <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE, convert = TRUE) 
d3 <- qReturn[["return"]][["workCount"]]

# Finally gather in a df 
typeDF <- data.frame(grounding = c("Demonstration model", "Data-based model", "Science-based model"), freq = c(d1, d2, d3))
```

```{r include=FALSE}
# create a percentage column
typeDF$freq <- as.numeric(as.character(typeDF$freq))
typeDF <- mutate(typeDF, percentage = round((freq/sum(freq))*100, 1))
```

```{r}
typeDF %>%
  kbl(caption = "Simulation model grounding") %>%
  kable_paper(full_width = F)
```





#### Pedagogies


```{r}
query = 'SELECT ?pedagogy (COUNT(?work) AS ?count)
        WHERE
	{ ?work :pedagogy ?pedagogy }
GROUP BY ?pedagogy  
ORDER BY ?pedagogy ' 
pdgTable <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE)
prtTable <- as.data.frame(pdgTable[1])
colnames(prtTable) <- c("pedagogy", "count")
```

```{r include=FALSE}
# Stripp of URIs
prtTable <- data.frame(stripOffNS(prtTable))
prtTable$pedagogy <- fragment(prtTable$pedagogy)
```


```{r include=FALSE}
# create a percentage column
prtTable$count <- as.numeric(as.character(prtTable$count))
prtTable <- mutate(prtTable, percentage = round((count/sum(count))*100, 1))
```

```{r}
prtTable %>%
  kbl(caption = "Pedagogies") %>%
  kable_paper(full_width = F)
```

 

### Learning time
Learning time is an important parameter, but by far not all studies mention learning time precisely. We coded learning time in a format starting with the capital letter P (for Period) and then the amount of minutes (M), hours (H), or days (D): P30M is 30 minutes, P2H30M is 2 hours 30 minutes. (This follows the XML standard https://www.w3.org/TR/xmlschema11-1/). 

```{r}
query = 'SELECT ?duration (COUNT(?duration) as ?learningTime) WHERE {
            ?work :learningTime  ?duration . }
         GROUP BY ?duration '
timeTable <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE, convert= TRUE)
prtTable <- as.data.frame(timeTable[1])
colnames(prtTable) <- c("duration", "count")
```

```{r include=FALSE}
# create a percentage column
prtTable$count <- as.numeric(as.character(prtTable$count))
prtTable <- mutate(prtTable, percentage = round((count/sum(count))*100, 1))
```

```{r}
prtTable %>%
  kbl(caption = "Learning duration") %>%
  kable_paper(full_width = F)
```

### Research Methods 

```{r}
query = 'SELECT ?method (COUNT(?method) AS ?methodTotal)
        WHERE
	{?work :researchMethod ?method }
GROUP BY ?method  
ORDER BY ?method '
methodTable <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE)
prtTable <- as.data.frame(methodTable[1])
colnames(prtTable) <- c("method", "count")
```

```{r include=FALSE}
# Stripp of URIs
prtTable <- data.frame(stripOffNS(prtTable))
prtTable$method <- fragment(prtTable$method)
```


```{r include=FALSE}
# create a percentage column
prtTable$count <- as.numeric(as.character(prtTable$count))
prtTable <- mutate(prtTable, percentage = round((count/sum(count))*100, 1))
```

```{r}
prtTable %>%
  kbl(caption = "Research methods") %>%
  kable_paper(full_width = F)
```



### Effectiveness of interventions


```{r}
query = 'SELECT ?effect (COUNT(?effect) AS ?effectTotal)
        WHERE
	{ ?work :effectiveness ?effect }
GROUP BY ?effect  
ORDER BY ?effect '
effectTable <- evalQuery(rep,
  query = query, returnType = "dataframe",
  cleanUp = TRUE)
prtTable <- as.data.frame(effectTable[1])
colnames(prtTable) <- c("effectiveness", "count")
```



```{r include=FALSE}
# create a percentage column
prtTable$count <- as.numeric(as.character(prtTable$count))
prtTable <- mutate(prtTable, percentage = round((count/sum(count))*100, 1))
```

```{r}
prtTable %>%
  kbl(caption = "Effectiveness of interventions") %>%
  kable_paper(full_width = F)
```





